Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-07 journal paper/content/sec-theory.tex
Expanded the footnote re "a little greedy".

\item The modified algorithm does not record rewards received in steps with the ``greedy choice".%
    \footnote{This is probably not essential, but makes for a cleaner comparison between the two algorithms.}

>>>>

\item The modified algorithm does not record the ``greedy choice" steps in its data set.%
    \footnote{In other words: in the subsequent rounds, as far as the modified algorithm is concerned, the ``greedy choice" steps have never happened. While it is usually more efficient to consider all available data, this simplification enables a cleaner comparison between the two algorithms. Also, it makes for  a cleaner setup: otherwise, just to make the modified algorithm well-defined, we'd need to assume that \alg[1] is a mapping from step-$n$ histories to actions, for each step $n$. This is usually OK -- most bandit algorithms have this shape anyway -- but it prohibits \alg[1] to correlate its internal randomness across steps.}
